Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Continuous Online Learning-Based CSI Feedback in Massive MIMO Systems

@@

>>>>

\cite{liu2023continuous} tackles a critical limitation of deep learning (DL)-based CSI feedback in massive MIMO systems: the performance degradation caused by distribution shifts between training and real-world deployment scenarios. The authors propose a continuous online learning framework that addresses catastrophic forgetting while maintaining high feedback accuracy across diverse channel conditions.

@@

	\bibitem{liu2023continuous} 
	Y. Liu et al., 
	``Continuous Online Learning-Based CSI Feedback in Massive MIMO Systems,'' 
	\textit{IEEE Wireless Commun. Lett.}, 
	early access, 2023, doi: 10.1109/LWC.2023.10381825.
